HGP analysis: LFA

### 2019-05-01 RunAnalysis/2_run_lfa.Rmd
more git cleaning

```{r lfa}
tic()
LF <- lfa(data, 4)
toc()
message("lfa run complete")
```

```{r save}
tic()
saveRDS(LF, "./data/preprocessed/lf.rds")
toc()
```
```{r}
gcinfo(verbose = FALSE) #-- don't show it anymore
gc()
```

>>>>

```{r lfa}
tic()
LF <- lfa(data, 5)
toc()
message("lfa run complete")
```

```{r save}
tic()
saveRDS(LF, "./data/preprocessed/lf5.rds")
toc()
```
```{r}
gcinfo(verbose = FALSE) #-- don't show it anymore
gc()
```
